\section{Commonsense Knowledge}

Intelligent behavior is impossible without knowledge. As a learning system is out of the scope of this thesis, the knowledge useful for the robot has to be chosen and prepared. In this work commonsense knowledge about indoor environments, rooms and objects are important. Some knowledge, like the concept of a room, is used in the design of the system. Other knowledge, like visual appearance of objects and room types are coded in the weights of the CNNs, which are trained on thousands of labeled images. The last part of the commonsense knowledge given to the robot is the knowledge about the correlation between the type of a room and the objects located in the room.

The information about the room-type-object-correlation is used in two ways. First, it is used to improve the object probabilities at already seen locations. As the object probabilities might be still very uncertain at many locations after a short room exploration this helps to guide the robot to more promising areas when searching. Second, it is used to estimate the object probabilities in parts of a room not seen yet. This makes it possible to make a reasonable estimate of the probability of a searched object being in a room after peeking into the room. Therefore the search of unlikely rooms can be postponed and the robot can proceed in searching in more likely locations, which consequently reduces the expected search time. 

Only correlations between the detectable object classes and detectable room types have to be known. These are the classes the neural networks are trained for. With $|RT|$ room types and $|OT|$ object classes this results in a $|RT|$x$|OT|$ matrix $M$, where the element $M_{r,o}$ represents the probability of an object of type $o$ being in a room of type $r$. 

% Multiple ways of estimating the matrix elements were tried. 
% 
% One method is to extract the information from commonsense knowledgebases. While they contain lots of facts, these facts are only true or false and at best also a crude weight is attached specifying how believable the information is. To probability of an object of type $o$ being in a room of type $r$ can be estimated based on a similarity measure. This similarity measure is calculated using a singular value decomposition (SVD) on the matrix representing the information in the knowledge base like described in TODO (ref). However the results of this method were poor.
% 
% Another way to estimate the matrix elements is to gather the information from the internet. In TODO (Utilizing object-object and object-scene context when planning to find things) the probabilities were estimated based on the co-occurrence of tags on Flickr (ref) and TODO (Exploiting Probabilistic Knowledge under Uncertain Sensing for Efficient Robot Behaviour) used the number of hits in image search engines combined with information from the Open Mind Indoor Common Sense (OMICS) knowledgebase. Using the information from images on the internet has one downside. Common scenes are underrepresented while special combinations, like ducks in bathrooms, are highly overrepresented, which distort the results.

The idea is to use the information of image datasets created for computer vision challenges. The dataset the object detection neural network was trained on was used as there already exists information about the objects in the images. To get also the place categories of the images the used place classification CNN was run on all images of the dataset and the probability distribution over all place classes was stored for every image. With this information the matrix elements were calculated with
\begin{equation} \label{eq5_1}
    M_{r,o}=\frac{\sum_{i=1}^{|Images|}P_i(r)P_i(o)}{\sum_{i=1}^{|Images|}P_i(r)}
\end{equation}
where $P_i(r)$ is the probability of the image $i$ showing a place $r$ and 
\begin{equation} \label{eq5_2}
P_i(o)=\begin{cases}1 & if\; object\; in\; image\\0 & else\end{cases}
\end{equation}

This approach is more promising than other approaches, like the estimation based on the number of search results in image search engines. One reason is that the images in datasets used in computer vision challenges are intended to be representative for the world while on the Internet some uncommon scenes are highly overrepresented, like the duck in the bath tube. The second benefit is that the actual name of an object or room type class is not used, avoiding the problem of ambiguous terms. 

With this approach the meaning of the matrix M is slightly different. The matrix element $M_{r,o}$ is now the probability of an object of type $o$ being in an image taken in a room of type $r$. So the size of the space usually seen in an image and the size of the space, where the object probability should be estimated, have to be taken into account when using the information stored in the matrix $M$.

% \subsection{Room type co-occurrence} \label{ssec:num1}
% A crude estimate of the room type co-occurrence is sufficient in this thesis, as it is only used to improve the room type mapping by considering similar room types (like kitchen and kitchenette) and room types likely being side-by-side (like kitchen and dinner table). The estimation of this data is based on the similarity measure calculated from a commonsense knowledgebase. The conceptNet4 knowledgebase was used and the result is a 60x60 matrix, with values between 0 and 1.
