%%%% Time-stamp: <2013-02-25 10:31:01 vk>


\chapter*{Abstract}
\label{cha:abstract}

Everyday human environments have an underlying structure. Knowledge about this structure is used by humans to carry out tasks efficiently. In this thesis a robotic system is presented which uses such commonsense knowledge to execute an intelligent active object search in unknown open indoor environments. The main challenges are the selection of useful commonsense knowledge, the design of a suitable representation of the environment, and the development of a search planner which utilizes the gathered information. The concept of rooms, and commonsense knowledge about the connection between the room type of an area and the objects usually located in that area are utilized in this thesis. Using the commonsense knowledge, the room type of an area allows to estimate object probabilities in this area and the room type detected after peeking into a room allows to estimate the object probabilities in the whole room. A mapping system was developed which creates a semantic map of the environment containing the room structure and information about seen objects and room types of areas of the environment. This information is extracted from images using convolutional neural networks. Based on this map, a probabilistic planner generates view poses for the robot to drive to which minimize the expected search time. Test runs of the developed system showed a more intelligent behavior, where likely areas were searched first, and an improved performance compared to a coverage-maximizing search system. The findings of this work can be used in similar tasks with the goal to create robotic systems being able to help humans with a wide variety of tasks.


%This work proves again the potential of intelligent robotic systems, which utilize commonsense knowledge to execute tasks in everyday human environments more efficiently.

%\glsresetall %% all glossary entries should be used in long form (again)
%% vim:foldmethod=expr
%% vim:fde=getline(v\:lnum)=~'^%%%%\ .\\+'?'>1'\:'='
%%% Local Variables:
%%% mode: latex
%%% mode: auto-fill
%%% mode: flyspell
%%% eval: (ispell-change-dictionary "en_US")
%%% TeX-master: "main"
%%% End:
