\chapter{Conclusion and Future Work}

In this thesis an intelligent active object search system was presented. The information available about the search environment is important for an efficient execution of the object search. Therefore a hybrid, semantic mapping system was developed. The proposed hybrid map design which combines a topological representation of the room structure and separated semantic metric maps for each room, allows to split the search problem into two abstraction levels. Furthermore, the segmentation of the environment into rooms resulted in smaller metric maps which proved to be less prone to inaccuracies in the map creation procedure. The semantic maps of the rooms contain, in addition to occupancy information, information about where objects were seen, which is obtained using a CNN for object detection, and information about the room types of areas in the room which is obtained using a CNN for place classification. Using the information in the maps and the commonsense knowledge about the connection between room types and objects typically located there, likely object locations within a room and the probability of a searched object being in a room were estimated. This estimation is also possible in partially explored rooms, like after peeking into a room. The search is planned in two steps. At first the next room to search was selected based on the topological map and then the actual search was planned by a second planner which had only to consider the semantic metric map of the current room.

The generated maps appear reasonable, though an exact evaluation of the maps was not possible due to the lack of a reasonable ground truth. Comparisons with a coverage maximizing search system and the evaluation of the behavior of the robot using the proposed intelligent search system showed that this system improves the search performance, measured by the search time and the search path, significantly. However, also some problems and suboptimal behaviors were encountered. Basic components of the system, like the navigation and the object detection, were still far from being perfect and problems of those components had a negative impact on the overall search performance. Also the search system itself has much room for further improvements. The information in the maps was found to be vague and the search planning has especially problems to find a good balance between exploration and exploitation. This resulted in some suboptimal decision about what room should be searched next.

The way to a human-like search performance is still very long and a lot of further research in many different areas is needed to achieve this. Better object detection systems are necessary to find objects faster and more reliably. More accurate and more extensive commonsense knowledge about indoor environments can help to improve the reasoning about object locations and also the interaction with humans or other robots can help to find objects faster. Also more sophisticated search planning approaches are necessary which can better handle the complexity of the problem and the uncertainty of the sensor data and the commonsense knowledge. While there is much room for improvements, this work showed some promising ideas and the potential of intelligent robot behavior in everyday human environments.