\chapter{Evaluation}

In this chapter we present an evaluation of the active object search system described in this thesis. A detailed and meaningful quantitative evaluation of the complete system is very demanding for multiple reasons. The test conditions, like the environment, the searched object type, the object location and the starting pose, have a huge impact on the search time and the utility of an intelligent behavior. The result is also influenced by random factors, like measurement noise, inaccuracies of the robot movement and timing of actions, which can lead to very different results even with similar settings. Furthermore, test runs can easily take more than half an hour, so extensive testing needs time. Therefore this evaluation is mostly done qualitatively by investigating representative runs and discussing special cases.

The evaluation is split into three parts. The first part covers the basic functionality, where the results of the computer vision and the performance of the navigation are discussed. In the second part the quality of the generated maps is investigated. The last part covers the performance of the actual object search.

Three environments were available for testing. Environment 1 is a home environment in a small flat, consisting of three rooms. Environment 2 is an atypical university environment consisting of some offices, and a robotics lab. Environment 3 is a part of an university floor with rooms of various types. A more detailed description of the environments can be found in Section \ref{EvalMapping}. For a first testing of the active object search system, environments with more space for navigation and less clutter would be better to reduce the influence of disturbing factors, like navigation problems, on the test results. As such environments were not available the robot has to cope with the difficulties and these have to be considered in the results. Some minor modifications were made to the environments, like fencing off obstacles the robot cannot detect neither with the LIDAR nor with the camera and dangerous areas like stairs.

\input{Evaluation/BasicEval.tex}
\input{Evaluation/MappingE.tex}
\input{Evaluation/SearchEval.tex}
