\chapter{Introduction}

With technical progress in the field of robotics and related areas, autonomous robots are now able to execute many tasks in factories, even without modifications to the environment like painted lines. However, robots struggle to conquer everyday human environments. Domestic environments might seem very chaotic at the first glance, with a wide variety of different types of environments and huge differences in their appearance. However, those environments have an underlying structure which is used by humans all the time to carry out tasks efficiently. Indoor environments are usually segmented into rooms which are separated by walls and only connected by doors. A room consists of one or a small number of areas, where each area has specific purposes, e.g. a kitchen is used for baking and cooking. For each purpose specific objects are used, e.g. a pan for cooking which can be assumed to be somewhere around. 

The goal of this thesis is to equip a robot with commonsense knowledge about indoor environments to execute a task efficiently. The investigated task is to search an object in an unknown open indoor environment. This is a relative simple task, but can benefit a lot from commonsense knowledge about indoor environments, e.g. knowledge about room types and which objects are usually located in rooms of a certain type. It is also an essential skill for a robot working in domestic environments. Therefore, research on this topic will be useful to enable future robotic systems. During the execution of this task the robot has to find the best next view poses. In this thesis the best next view pose is the pose that minimizes the expected search time. The robot has to decide which areas are promising to contain the searched object. It also has to find a balance between exploration and the search of already explored areas because the environment is unknown at the start of a search. Here the commonsense knowledge is important to make better estimations about unseen or only vaguely seen areas. 

The system presented in this work uses a hierarchical approach. The environment is seen as a topology of rooms at a higher abstraction level and the details are handled for every room separately. Within a room convolutional neural networks (CNNs) for object detection and place classification are used to create semantic maps containing information about the positions where objects were seen and the room types of areas in the room. Using the results of the object detection, the place classification and the connection between the type of an area and the objects usually located in that area, object probabilities are estimated, even for not or only vaguely seen areas. To achieve this a new mapping system was developed, capable to create hybrid maps which combine the room topology and semantic maps of the rooms. The developed mapping system is also able to cope with the uncertain results of the sensors and the CNNs. The hybrid map is then used by the developed hierarchical search planner which first selects the next room to search and then plans the search within that room, to execute the search task efficiently. 

Similar systems were already developed, e.g. by Aydemir et al. \cite{main}. However, the generality of the used CNNs are a step towards the flexibility which will be necessary in future robots used for example in households. The proposed system was tested in common indoor environments, where the behavior was investigated and a comparison with a system using no commonsense knowledge was done.

\section{Challenges}

The development of an intelligent active object search system poses various challenges. The main questions to answer during the development were:
\begin{itemize}
 \item \textbf{What commonsense knowledge can be used to execute the object search intelligently:} Not only useful types of commonsense knowledge have to be found, but also ways to obtain and represent the knowledge.
 \item \textbf{What information the robot should gather and what sensors are necessary for that:} This includes not only the question of how to detect objects, but also what data is necessary for the navigation and the application of the commonsense knowledge. Also suitable sensors have to be found.
 \item \textbf{How the gathered information about the environment should be represented:} This involves the design of a semantic map representation which contains all the gathered information. This design has to take into account the types and quality of the incoming data and has also to be suitable for the planning of the search.
 \item \textbf{How the search planning, using this knowledge, should be done:} The questions are how to use the gathered knowledge and especially how to handle the complexity of the active object search problem.
\end{itemize}

To reduce the amount of work suitable existing software packages have to be found and if necessary adapted. Furthermore, as this is a robotic system, many unexpected problems occur during the developed of the active object search system which have to be solved.

\section{Contribution}

In this thesis an intelligent object search system is presented and evaluated which can efficiently find objects of various different types in indoor environments. A hybrid semantic map design was therefore developed which represents the room structure of the environment as a topological map and the details of each room as separated semantic metric maps. These room maps contain, in addition to occupancy information, also information about detected objects and the room types of areas in the room. The developed system is also able to estimate object probabilities in vaguely seen areas and in partially explored rooms, using the information about the room types and commonsense knowledge about the connection between room types and objects usually located there. Furthermore, a hierarchical search planner was developed which in a first step selects the optimal next room to search based on the estimated object probabilities and the expected search times in the rooms and in a second step plans the search within the chosen room, where likely object locations are searched first. This enables the robot to search in likely rooms and room areas first and to postpone the search in unlikely rooms.

\section{Outline}

The structure of this thesis is as follows. In Chapter 2 a formal representation of the problem is given. Chapter 3 covers related research on the topic of active object search and its subproblems and Chapter 4 contains information about basic components used in this work. Chapter 5 describes the concept of the proposed active object search system, while Chapter 6 focuses on the Implementation of the concept. In Chapter 7 the results of the evaluation are presented. Finally, Chapter 8 contains a summary of the thesis, a discussion of the results and possible future work on this topic.