\section{GMapping}

GMapping \cite{GMapping} is an open-source library implementing two dimensional simultaneous localization and mapping (SLAM). The sensor data used by GMapping are range measurements from a light detection and ranging sensor (LIDAR) and odometry data. 

SLAM is a difficult problem because for the creation of a map the pose of the robot is necessary and for accurate localization a map is necessary. GMapping implements a Rao-Blackwellized particle filter \cite{particle} to solve this chicken-and-egg problem. The SLAM problem is split into two parts, the estimation of the trajectory and the mapping given the trajectory. The probability distribution over the trajectories is represented by a particle filter. Each particle in the particle filter has a weight and its own map, which is created by occupancy grid mapping with known pose. 

The particle filter algorithm consists of three steps, sampling, importance weighting and resampling. In the sampling step the poses of the particles are updated by a movement step sampled from a proposal distribution. This proposal distribution is based on the odometry data and in more sophisticated systems further sensor data. In the importance weighting step a weight is assigned to each particle representing the likelihood that the particle represents the true trajectory. In the resampling step particles with low weight are replaced by particles with a higher weight. This step is needed as a continuous distribution is approximated by only a finite number of particles. After the resampling the maps of the particles are updated using the particle pose and the range measurements from the LIDAR.

The problem of this approach is the high computational cost when using a large number of particles, which is usually needed for a good representation of the distribution over the trajectories. Therefore, GMapping also takes the range measurements into account in the sampling step. This way unlikely particle poses can be ruled out immediately and a much lower particle number is sufficient. GMapping also uses a sophisticated resampling technique, which only does resampling if necessary. This reduces the probability of discarding good particles, which is especially important for low particle numbers.