\section{ROS Robot Operating System} \label{ROS}

Robot Operating System (ROS) \cite{ROS} is an open-source robotics framework. It provides a structured communication layer for interprocess communication. As TCP-IP sockets are used, the processes can also run on different machines, so outsourcing of computational heavy tasks to off-board computers and communication between multiple robots can easily be done with ROS. ROS also includes the \texttt{tf} transformation system. The \texttt{tf} system collects coordinate transformations and constructs a dynamic transformation tree. Using this transformation tree the \texttt{tf} system can provide transformations between all coordinate frames in the transformation tree. It is also able to handle changing transformations, like transformations between joints of a robot arm, and can interpolate between transformations at different times. Furthermore, ROS includes build tools and tools for package managing. This makes the usage of third party packages, contributed by members of a big community, easy. These packages range from ROS-wrappers for device drivers and software libraries to complete implementations of algorithms. ROS supports multiple programming languages, the most important are C++ and Python.

A robotics system using ROS is typically split into multiple processes, called nodes, where each node executes an individual task. Different ways for the communication between the nodes are available in ROS. The most important one are messages, which are predefined data-structures, which can hold information described through the interface definition language (IDL). The messages can be published on and received from topics, which are named data channels. The topics are managed by a special node, the ROS master, which also keeps track of all the running nodes. As ROS uses peer-to-peer communication, the ROS master is only responsible for setting up connections between the nodes, but not for the data transmission. Before a node can publish on a topic, the topic has to be advertised and before a message of a certain topic can be received the node has to subscribe to the topic. A topic can be advertised by multiple nodes and also multiple nodes can subscribe to a topic. The most important property of messages is that the sender of a message has no knowledge about the receiving nodes and if the messages are processed by the receivers.

A second way of communication between nodes are services. Services are used for synchronous communication, where a request is sent to another node and a response is sent back after the request is processed. The structure of the request and the response are also described through the IDL. The \texttt{actionlib} package enables a third way of communication. Using messages the functionality of services is implemented, with the additional possibility for feedback during the execution. This is especially useful during long-lasting tasks.